Performance Optimization of Service Chain \\for vCPE in Small Size Network \\with OpenFlow Switch

### 2017-02-24 netsoft_paper.tex
modify QoS decription

\section{System Description}
\subsection{Overview of Network Function}
With the concept of SDN-enabled VNFs, SDN technology work not only for traffic steering but also as a part of network functions. In this idea, network functions have been achieved by the synergies between computer and network infrastructures, shown in Fig. \ref{fig:desc_nfv_overview}. The former is a VNF controller, mainly responsible for dealing with stateful processing. The latter is a SDN switch, used for stateless processing.

@@

\begin{itemize}[\IEEEsetlabelwidth{Z}]
\item For a specific host.
\item For a specific application.
\item For a specific application from a host or a domain.
\end{itemize}

@@

\subsection{Multiple Flow Tables Strategy}
In subsection A , the vCPE service design architecture have been introduced. The network functions are handled by the cooperation between SDN controller on cloud and SDN switch at the local network gateway. The controller transform the network functions to series of OpenFlow rules requests and send to SDN switch. Following the orders from controller, the SDN switch inserts rules to its flow tables, checks incoming packets against the flow entry match fields, and execute the actions in matching rules. The flow table defines all matching and corresponding processing, thus playing an important role to executive network function.

@@

The network functions of vCPE services including Firewall, NAT, DHCP, QoS and Forwarding. We have determined the order of each function, shown in \ref{fig:mft_table_overview}. (Notice that the flow tables are counting from zero) In the following subsections, we will introduce how to implement these network functions, which type of rules will be inserted to SDN switch, and how these rules affect our decision of the order of flow tables.

@@

@@

\subsubsection{Rate limitation of applications}
There are more and more network’s applications used such as online games, video streaming, conference call, etc. Therefore, there are massive traffic working in the network. Consequently, we integrate with a flow classification engine to identify the flow belongs which application is.
However, an application may have many connections, we will equally distribute the bandwidth to each connection.

For instance, if there is an application and we can find out which flows belong to this application through the flow classification engine. If we want to limit this application to 1000Kbps. As Figure. \ref{fig:mft_qos_rate_app}, in T0, we know there are 3 connections belong this application and we will set the bandwidth of meter to each link with 1000/3 = 333Kbps. In T2, there are more two connections added to this application and we will reset the bandwidth of meter to each links with 1000/5 = 200Kbps. In T2, there is a connection ended by this application, we will reset the bandwidth of meter to each links with 1000/4 = 250Kbps, therefore. Whereas, the sum of bandwidth from this application is always being 1000 Kbps. That is, the bandwidth will be dynamically adjusted.

@@

\subsubsection{Rate limitation for a certain application of certain host}

By way of flow classification, we can know the 5 tuple (IP protocol, source IP, destination IP, source port, destination port) from each connection between an application and a host. Consequently, the network administrator can use those 5-tuple and dynamically adjust the bandwidth of meter, according the algorithm mentioned in above, to limit the bandwidth of each application from a host.
As shown in figure. \ref{fig:mft_qos_rate_host_app}. In T0, we want to limit the application B to the Host with 600 Kbps and we will add the rules matching each 5 tuples from application A and set Meter 1 to those rule. In the meantime, the bandwidth of Meter 1 is set to 600/N Kbps if there are N connections built from application B of the host.
In T1, marked as (a), If we want to limit the application A to the Host with 300 Kbps, we will add the rules matching each 5 tuples from application A and set Meter 2 to those rule.
Then in T2, marked as (b), application B has already been limited since T0 and we want to change the bandwidth of application B from 600Kbps to 1000 Kbps.
However, We would not change the rule in flow table, we only change the bandwidth of the correspond meter in the meter table. That is, the bandwidth of Meter 1 will be set from 600/N to 1000/N. Therefore, there only have a little overhead between switch and controller. That is, if there are Ni connections in time Ti, then the bandwidth will be set as shown as following.
Similarly, we can use the same way to limit the whole network while not only to the specific host.

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{./figures/mft_qos_rate_host_app}
\caption{Illustration of rate-limiting for a certain application of certain host}
\label{fig:mft_qos_rate_host_app}
\end{figure}

\subsubsection{The flow table order of QoS service}
QoS service is located at flow table 2, because the location of NAT/DHCP, firewall are determined. Here we only need to decide the arrangement of QoS and forwarding.
Let's consider the scenario that we put the QoS flow table after the forwarding flow table. Plus, we have only two services enabled, forwarding and QoS, then suppose a host is not limited by QoS policies. The very first packet will not be affected in both arrangement. For the following packets, the difference can be observed. The packets which has matched the rules of the forwarding flow table will still cause packet-ins when they go to QoS flow table. This is not supposed to happen, since the host is not restrained by QoS policies and any packet-in increase the controller's load.
To reduce the burden of the controller, we put QoS flow table ahead of forwarding flow table. In this scenario, all packets that pass through QoS flow table will continue to go to forwarding flow table without matching any QoS rules. Then the packets except the very first packet will just be forwarded by forwarding service instead of causing packet-ins. Hence the controller's load will decrease. To use our system, the forwarding service is necessary, so there is no such scenario that users enable QoS and disable forwarding.

\subsection{Forwarding}
In this service, when the first packet in a new connection incoming, it will cause a packet-in event because there is no corresponding rule. When controller receives the packet, it will record IP-layer information, including source IP, destination IP, input port number, source mac address and destination mac address. With the recorded information, the controller is able to install a 5-tuple forwarding rule for this connection and following packets don’t need to packet-in again. The 5-tuple is source IP, destination IP, network layer protocol, source layer 4 port, and destination layer 4 port.

@@

\section{Conclusion and future works}

>>>>

\section{System Description}
\subsection{Overview of Network Function}\label{ssec:desc_nfv_overview}
With the concept of SDN-enabled VNFs, SDN technology work not only for traffic steering but also as a part of network functions. In this idea, network functions have been achieved by the synergies between computer and network infrastructures, shown in Fig. \ref{fig:desc_nfv_overview}. The former is a VNF controller, mainly responsible for dealing with stateful processing. The latter is a SDN switch, used for stateless processing.

@@

\begin{itemize}[\IEEEsetlabelwidth{Z}]
\item For a specific host.
\item For a specific application.
\end{itemize}

@@

\subsection{Multiple Flow Tables Strategy}
In subsection \ref{ssec:desc_nfv_overview}, the vCPE service design architecture have been introduced. The network functions are handled by the cooperation between SDN controller on cloud and SDN switch at the local network gateway. The controller transform the network functions to series of OpenFlow rules requests and send to SDN switch. Following the orders from controller, the SDN switch inserts rules to its flow tables, checks incoming packets against the flow entry match fields, and execute the actions in matching rules. The flow table defines all matching and corresponding processing, thus playing an important role to executive network function.

@@

The network functions of vCPE services including Firewall, NAT, DHCP, Forwarding and QoS. We have determined the order of each function, shown in \ref{fig:mft_table_overview}. (Notice that the flow tables are counting from zero) In the following subsections, we will introduce how to implement these network functions, which type of rules will be inserted to SDN switch, and how these rules affect our decision of the order of flow tables.

@@

\subsection{Forwarding} \label{ssec:forwarding}
In this service, when the first packet in a new connection incoming, it will cause a packet-in event because there is no corresponding rule. When controller receives the packet, it will record IP-layer information, including source IP, destination IP, input port number, source mac address and destination mac address. With the recorded information, the controller is able to install a 5-tuple forwarding rule for this connection and following packets don’t need to packet-in again. The 5-tuple is source IP, destination IP, network layer protocol, source layer 4 port, and destination layer 4 port.

@@

\subsubsection{Rate limitation of applications}
There are more and more network’s applications used such as online games, video streaming, conference call, etc. Therefore, there are massive traffic working in the network. Consequently, we integrate with a flow classification engine to identify the flow belongs which application is. The integration scenario will be shown as Fig. \ref{fig:class_classifying}.

In order to rate limit for a certain application, we need to gathering per-flow statistics information first. When
a connection is created, the first packet of this connection will be handled by the forwarding service and add 5-tuple rules into SDN switch, so we can get the bandwidth information of per-flow connection. (See subsection \ref{ssec:forwarding} for details). With the classified result of application identification, we can know the application type of each connection.

When network administrator request to rate limit a certain application to a certain bandwidth, we will equally distribute the bandwidth to each connection of the application. The controller set all flows belong to the same application into the same meter, and modifying the bandwidth of meter to achive our goal. For instance, if there is an application and we can find out which flows belong to this application through the flow classification engine and we want to limit this application to 1000Kbps. As Figure. \ref{fig:mft_qos_rate_app}, in T0, we know there are 3 connections belong this application and we will set the bandwidth of meter to each link with 1000/3 = 333Kbps. In T2, there are more two connections added to this application and we will reset the bandwidth of meter to each links with 1000/5 = 200Kbps. In T2, there is a connection ended by this application, we will reset the bandwidth of meter to each links with 1000/4 = 250Kbps, therefore. Whereas, the sum of bandwidth from this application is always being 1000 Kbps. That is, the bandwidth will be dynamically adjusted.

@@

\subsubsection{The flow table order of forwarding and QoS service}
Since the location of NAT, DHCP and firewall are determined. Here we only need to decide the arrangement of QoS and forwarding.
Let's consider the scenario that we put the QoS flow table after the forwarding flow table. Plus, we have only two services enabled, forwarding and QoS, then suppose a host is not limited by QoS policies. The very first packet will not be affected in both arrangement. For the following packets, the difference can be observed. The packets which has matched the rules of the forwarding flow table will still cause packet-ins when they go to QoS flow table. This is not supposed to happen, since the host is not restrained by QoS policies and any packet-in increase the controller's load.
To reduce the burden of the controller, we put QoS flow table ahead of forwarding flow table. In this scenario, all packets that pass through QoS flow table will continue to go to forwarding flow table without matching any QoS rules. Then the packets except the very first packet will just be forwarded by forwarding service instead of causing packet-ins. Hence the controller's load will decrease. To use our system, the forwarding service is necessary, so there is no such scenario that users enable QoS and disable forwarding.

@@

\section{Conclusion and future works}
(Eric)
